Analytic Occultation Light Curves in Reflected Light

### 2020-04-06 tex/ms.tex
fix backend

\section{The Solution: Occultation}
\label{sec:solution-occ}
%
The integration in the unocculted case presented above is relatively
straightforward, since
the boundaries of integration are always the half-ellipse defining the
terminator and the half-circle defining the upper limb of the body
(Equation~\ref{eq:rT}). When an occultor is present, however, the
integration boundaries are far less trivial, since they may or may not
include sections of the terminator, sections of the limb of the body,
and sections of the limb of the occultor. There are in total eight families of
configurations, each defined by a distinct combination of integration
boundaries; these are shown in Figure~\ref{fig:cases}.
Together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position.

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight families of cases of occultations in reflected light.
            In these figures, the body with the solid outline
            is the one whose flux we are interested in, and the body with the
            dashed outline is the occultor.
            The night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted).
            The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the orange boundary (the curves
            $P$, $T$, and $Q$ of
            \S\ref{sec:cases-5-8}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

@@

Case 5 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 6--8 involve two points of intersection between the occultor limb and
the terminator. Case 6 corresponds to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. We begin by computing the
flux over the unocculted region, $f_3$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Cases 7 and 8 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 7
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{proof}{}
    \label{eq:7}
    f_7 = f_I - f_S
    \quad.
\end{proof}
%
Conversely, case 8 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_S
    \quad.
\end{proof}
%

@@

Pathological cases with 3 or 4 roots here (Figure~\ref{fig:pathological}).

>>>>

\section{The Solution: Occultation}
\label{sec:solution-occ}
%
The integration in the unocculted case presented above is relatively
straightforward, since
the boundaries of integration are always the half-ellipse defining the
terminator and the half-circle defining the upper limb of the body
(Equation~\ref{eq:rT}). When an occultor is present, however, the
integration boundaries are far less trivial, since they may or may not
include sections of the terminator, sections of the limb of the body,
and sections of the limb of the occultor. There are in total ten families of
configurations, each defined by a distinct combination of integration
boundaries; these are shown in Figures~\ref{fig:cases} and
\ref{fig:pathological}.
Together, these cases encompass all possible
occultation configurations, for any illumination angle, occultor size, and
occultor position.

\xxx{In general, we do not just integrate over the dayside.}

@@

\begin{figure}[t!]
    \begin{centering}
        \includegraphics[width=\linewidth]{figures/cases.pdf}
        \oscaption{cases}{%
            The eight principal families of cases of occultations in
            reflected light.
            In these figures, the body with the solid outline
            is the one whose flux we are interested in, and the body with the
            dashed outline is the occultor.
            The night side of the occulted body is colored
            black (dark grey if occulted), and the dayside is colored blue
            (light grey if occulted).
            The cases in the top row involve
            configurations in which the limb of the occultor does not intersect
            with the terminator at any point, so the visible flux may be
            computed in terms of classical \starry integrals. The remaining
            cases require integration along the orange boundary (the curves
            $P$, $T$, and $Q$ of
            \S\ref{sec:cases-5-8}), which
            include the terminator. These involve the evaluation of incomplete
            elliptic integrals and are derived below.
            \label{fig:cases}
        }
    \end{centering}
\end{figure}

@@

Case 5 corresponds to configurations in which the limb of the occultor
intersects the terminator at a single point. The integration region
(see Figures~\ref{fig:cases} and \ref{fig:geometry}) is the occulted
portion of the dayside, which is bounded by all three curves $P$, $Q$, and $T$.
The total flux may
be computed by subtracting the occulted flux $f_S$ from the total dayside
flux $f_0$:
%
\begin{proof}{}
    \label{eq:f5}
    f_5 = f_0 - f_S
    \quad.
\end{proof}
%
Cases 6--8 involve two points of intersection between the occultor limb and
the terminator. The region we integrate over is bounded only by the terminator
and the limb of the occultor, so when computing $f_S$ below we set
$\mathfrak{q}^\top = \boldsymbol{0}$.
%
Case 6 corresponds to occultors that block some of the
nightside and some of the dayside, but \emph{neither} of the extrema of the
terminator ellipse. We begin by computing the
flux over the unocculted region, $f_3$, which includes the spurious
nightside contribution. We then remove this contribution by noting that it
is equal to the total nightside contribution, $\hat{f}_0$, minus the
occulted nightside flux, $f_S$:
%
\begin{proof}{}
    \label{eq:f6}
    f_6 = f_I - (\hat{f}_0 - f_S)
    \quad.
\end{proof}
%
Cases 7 and 8 correspond to occultors that also block some nightside and some
dayside, along with \emph{both} of the extrema of the ellipse; these are
therefore exclusively for large occultors ($r_o > 1$). Case 7
involves occultations in which only a small lens-shaped region of the
nightside is visible. The total flux is the visible dayside plus unphysical
nightside contribution, $f_I$, minus the nightside contribution, which we
compute from Equation~(\ref{eq:fS}):
%
\begin{proof}{}
    \label{eq:7}
    f_7 = f_I - f_S
    \quad.
\end{proof}
%
Conversely, case 8 involves occultations in which only a small lens-shaped
region of the dayside is visible. In this case, we may compute the observed
flux from Equation~(\ref{eq:fS}) directly:
%
\begin{proof}{}
    \label{eq:f8}
    f_8 = f_S
    \quad.
\end{proof}
%

@@

Finally, cases 9 and 10 correspond to (rare) configurations involving three
or four roots to Equation~\ref{eq:quartic}, respectively, and are
illustrated in Figure~\ref{fig:pathological}.
